Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-05 paper/paper.tex
cite depireux

On the other hand, the field of music psychology investigates timbre with the aim of discovering its physiological and behavioral foundations \ml{vl cite}.
In this setting, prior knowledge, however accurate, of instrumentation does not suffice to conduct a study.
Rather, each excerpt must be played back to multiple human listeners.
Yet, collecting subjective responses to acoustic stimuli is a tedious and unscalable procedure, thus restricting the size of the musical corpus under study.
Such restriction hampers the applicability of iterative representation learning algorithms, such as stochastic gradient descent in artificial neural networks.
Nevertheless, advanced methods in electrophysiology allow to observe the firing patterns of biological neurons in the presence of controlled stimuli.
This observation, originally carried out on the ferret, has led to a comprehensive mapping of the primary auditory cortex, in terms of its spectrotemporal receptive fields (STRF) \ml{vl citer, dire que c'est du coup une base solide de représentation et que le modèle mathamtique que l'on utilisera ici est quasi equivalent}.

\ml{parler des travaux de Mounia}

>>>>

On the other hand, the field of music psychology investigates timbre with the aim of discovering its physiological and behavioral foundations \ml{vl cite}.
In this setting, prior knowledge, however accurate, of instrumentation does not suffice to conduct a study.
Rather, each excerpt must be played back to multiple human listeners.
Yet, collecting subjective responses to acoustic stimuli is a tedious and unscalable procedure, thus restricting the size of the musical corpus under study.
Such restriction hampers the applicability of iterative representation learning algorithms, such as stochastic gradient descent in artificial neural networks.
Nevertheless, advanced methods in electrophysiology allow to observe the firing patterns of biological neurons in the presence of controlled stimuli.
This observation, originally carried out on the ferret, has led to a comprehensive mapping of the primary auditory cortex, in terms of its spectrotemporal receptive fields (STRF) \cite{depireux2001amphyssoc}.

% \ml{vl citer, dire que c'est du coup une base solide de représentation et que le modèle mathamtique que l'on utilisera ici est quasi equivalent}.

%\ml{parler des travaux de Mounia}
